Sleep, relative to wake, increases both veridical and false memory in the DRM paradigm:

### 2023-07-11 manuscript.Rmd
Split up package activation to diagnose the problem

packagelist <- c('bookdown','knitr','rmarkdown','osfr','plyr','tidyr','dplyr','emmeans','ggplot2','Rmisc','buildmer','lme4','lmerTest','stringr','effects','effectsize','ggdist','car','gridExtra','kableExtra','rstatix','LSAfun','simr','effsize','readr')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

>>>>

# packagelist <- c('bookdown','knitr','rmarkdown','osfr','plyr','tidyr','dplyr','emmeans','ggplot2','Rmisc','buildmer','lme4','lmerTest','stringr','effects','effectsize','ggdist','car','gridExtra','kableExtra','rstatix','LSAfun','simr','effsize','readr')
# missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
# if (length(missingpackages)>0){install.packages(missingpackages)}
# toinstall <- packagelist[which(!packagelist %in% (.packages()))]
# invisible(lapply(toinstall,library,character.only=TRUE))

@@

``` {r activate1}

library(bookdown)
library(knitr)
library(rmarkdown)
library(osfr)
library(plyr)

``` {r activate2}

library(tidyr)
library(dplyr)
library(emmeans)
library(ggplot2)
library(Rmisc)

``` {r activate3}

library(buildmer)
library(lme4)
library(lmerTest)
library(stringr)
library(effects)

``` {r activate4}

library(effectsize)
library(ggdist)
library(car)
library(gridExtra)
library(kableExtra)

``` {r activate5}

library(rstatix)
library(LSAfun)
library(simr)
library(effsize)
library(readr)
